On exponential sums arising from the classical doubling method

### 2025-04-02 main.tex
more explicit matrices in unitary case

The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate $\rho$ in the table below.

@@

		where explitely $\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}$ refers to the torus

@@

x_0 & 0\\
0 & y_0

@@

	F(x_0) & 0\\
	0 & F(y_0)
	\end{pmatrix} \right) \in \restrictionOfScalars{\quadraticExtension}{\finiteField}{GL}_n

@@

		with character $\alpha(x_0)\alpha^{-q}(y_0)$.

>>>>

The idea behind the proof of \Cref{lem:indep_geo_conj} is that the formula from \Cref{thm:computation-of-doubling-gauss-sum-scalar-for-deligne-lusztig-characters} relates $\dblVirtualJacobiSumScalar{R_{T, \theta}}{\chi}/R_{T,\theta}(1)$ to $g_{T,\rho}(\chi,\theta,\psi)$ for the appropriate \calvin{doubling representation} $\rho$ in the table below.

@@

		where explitely $\finiteFieldExtension{n}^\times \times \finiteFieldExtension{n}^\times,\alpha \times \alpha^{-q}$ refers to the torus character pair

@@

x_0 & 0 & 0 & 0 & \hdots & 0 \\
0 & y_0 & 0 & 0 & \hdots & 0 \\
0 & 0 & F^2(x_0) & 0 & \hdots & 0 \\
0 & 0 & 0 & F^2(y_0) & \hdots & 0 \\
\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
0 & 0 & 0 & 0 & \hdots & F^{n-2}(y_0) \\

@@

	F(x_0) & 0 & 0 & 0 & \hdots & 0 \\
	0 & F(y_0) & 0 & 0 & \hdots & 0 \\
	0 & 0 & F^3(x_0) & 0 & \hdots & 0 \\
	0 & 0 & 0 & F^3(y_0) & \hdots & 0 \\
	\vdots & \vdots & \vdots & \vdots & \ddots & \vdots \\
	0 & 0 & 0 & 0 & \hdots & F^{n-1}(y_0) \\
	\end{pmatrix} \right)

@@

		mapping to $\alpha(x_0)\alpha^{-q}(y_0)$.
